---
title: "simDf"
---

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(servevolleyR)
```

This function converts the detailed lists returned (when `detail=TRUE`) in the following functions:

* [simGame](simGame.html)
* [simGames](simGames.html)
* [simSet](simSet.html)
* [simSets](simSets.html)
* [simMatch](simMatch.html)
* [simMatches](simMatches.html)

and converts them into a dataset with meta data about players, points, games, and sets.

### Usage

```{r eval = FALSE}
simDf(object)
```

When converting an object returned by `simGames`, `simSets` and `simMatches`, I recommend adding `plyr`'s progress bar, `.progress = "text"`, to `simDf` as large number of simulations will take a while to convert to a dataset.

```{r eval=FALSE}
simDf(object, .progress = "time")
```

<hr>

## `simGame` and `simGames`

A look at the dataset returned by `simGame` and `simGames`, only small number of simulations

```{r}
egGame <- simGame(p = .78, p2 = .56, firstServe = .67, detail = TRUE)
egGames <- simGames(n = 10, p = .78, p2 = .56, firstServe = .67)

egGame <- simDf(egGame)
head(egGame)

egGames <- simDf(egGames)
head(egGames)
```
The variables in each dataset are effectively the same, except `simGames` dataset has a variable **simNo** to identify the unique simulations, a look at those variables:

variables | about
----------|------
simNo | simulation number
player | player name
p | probability of server winning a point on their first serve
p2 | probability of server winning a point on their second serve
firstServe | probability of first serve being in
result | game result (1 if server wins, 0 if returner wins)
server | number of points won by server in service game
returner | number of points won by returner in service game

<hr>

## `simSet` and `simSets`

A look at the dataset returned by `simSet` and `simSets`, only a small number of simulations.

```{r}
egSet <- simSet(pA = .78, pB = .70, p2A = .56, p2B = .6,
                firstServeA = .67, firstServeB = .7, detail = TRUE)
egSets <- simSets(n = 10,
                  pA = .78, pB = .70, p2A = .56, p2B = .6,
                  firstServeA = .67, firstServeB = .7)

egSet <- simDf(egSet)
head(egSet)

egSets <- simDf(egSets)
head(egSets)
```

The variables in each dataset are similar to those found in the returned datasets from `simGame` and `simGames`, a look at those variables:

variables | about
----------|------
simNo | simulation number
pA | player A
pB | player B
setA | games won by player A
setB | games won by player B
set_res | set result (1 if player A wins, 0 if player B wins)
gameNo | game number in set
serving | player serving
p | probability of server winning a point on their first serve
p2 | probability of server winning a point on their second serve
firstServe | probability of first serve being in
game_res | game result (1 if server wins, 0 if returner wins)
server | number of points won by server in service game
returner | number of points won by returner in service game

<hr>

## `simMatch` and `simMatches`

A look at the dataset returned by `simMatch` and `simMatches`, only a small number of simulations.

```{r}
egMatch <- simMatch(sets = 3, finalSetTiebreak = TRUE, detail = TRUE,
                    pA = .78, pB = .70,
                    p2A = .56, firstServeA = .67,
                    p2B = .6, firstServeB = .7)
egMatches <- simMatches(n = 10, sets = 3,
                        pA = .78, pB = .70,
                        p2A = .56, firstServeA = .67,
                        p2B = .6, firstServeB = .7)

egMatch <- simDf(egMatch)
head(egMatch)

egMatches <- simDf(egMatches)
head(egMatches)
```

The variables in each dataset are similar to those found in the returned datasets from `simSet`, `simSets`, `simGame` and `simGames`, a look at those variables:

variables | about
----------|------
simNo | simulation number
playerA | player A (who started the match serving)
playerB | player B (who started the match returning)
mA | sets won by player A
mB | sets won by player B
result | match result, (1 if player A wins, 0 otherwise)
setNo | set number
pA | player A (who started the set serving)
pB | player B (who started the set returning)
setA | games won by player A
setB | games won by player B
set_res | set result (1 if player A wins, 0 if player B wins)
gameNo | game number in set
serving | player serving
p | probability of server winning a point on their first serve
p2 | probability of server winning a point on their second serve
firstServe | probability of first serve being in
game_res | game result (1 if server wins, 0 if returner wins)
server | number of points won by server in service game
returner | number of points won by returner in service game


<a href="https://github.com/durtal/servevolleyR" class="github-corner"><svg width="80" height="80" viewBox="0 0 250 250" style="fill:#d9230f; color:#fcfcfc; position: absolute; top: 0; border: 0; right: 0;"><path d="M0,0 L115,115 L130,115 L142,142 L250,250 L250,0 Z"></path><path d="M128.3,109.0 C113.8,99.7 119.0,89.6 119.0,89.6 C122.0,82.7 120.5,78.6 120.5,78.6 C119.2,72.0 123.4,76.3 123.4,76.3 C127.3,80.9 125.5,87.3 125.5,87.3 C122.9,97.6 130.6,101.9 134.4,103.2" fill="currentColor" style="transform-origin: 130px 106px;" class="octo-arm"></path><path d="M115.0,115.0 C114.9,115.1 118.7,116.5 119.8,115.4 L133.7,101.6 C136.9,99.2 139.9,98.4 142.2,98.6 C133.8,88.0 127.5,74.4 143.8,58.0 C148.5,53.4 154.0,51.2 159.7,51.0 C160.3,49.4 163.2,43.6 171.4,40.1 C171.4,40.1 176.1,42.5 178.8,56.2 C183.1,58.6 187.2,61.8 190.9,65.4 C194.5,69.0 197.7,73.2 200.1,77.6 C213.8,80.2 216.3,84.9 216.3,84.9 C212.7,93.1 206.9,96.0 205.4,96.6 C205.1,102.4 203.0,107.8 198.3,112.5 C181.9,128.9 168.3,122.5 157.7,114.1 C157.9,116.9 156.7,120.9 152.7,124.9 L141.0,136.5 C139.8,137.7 141.6,141.9 141.8,141.8 Z" fill="currentColor" class="octo-body"></path></svg></a><style>.github-corner:hover .octo-arm{animation:octocat-wave 560ms ease-in-out}@keyframes octocat-wave{0%,100%{transform:rotate(0)}20%,60%{transform:rotate(-25deg)}40%,80%{transform:rotate(10deg)}}@media (max-width:500px){.github-corner:hover .octo-arm{animation:none}.github-corner .octo-arm{animation:octocat-wave 560ms ease-in-out}}</style>
