---
title: "simGames"
---
```{r echo=FALSE, warning=FALSE, message=FALSE}
library(servevolleyR)
```

Simulate many service games given a number of parameters for the server, that include probability of the server winning a point on their first serve, on their second serve, and the probability that their first serve will go in, returning a detailed list.

### Usage

```{r eval=FALSE}
simGames(n = 1e3, p, p2 = NULL, firstServe = NULL, detail = FALSE, player = "A")
```

### Arguments

param | details
------|--------
n | number of simulations (default is 1000)
p | probability of server winning point on their first serve
p2 | probability of server winning point on their second serve
firstServe | probability of first serve being in
player | player name
.progress | `plyr`'s  progress bar

### Return

`simGames` will return a detailed list, containing data about the simulated games rather than just the results of the simulations, this list can then be converted to a dataset using [simDf](simDf.html), an example dataset is show below.

### Methods

There are a number of generic methods available for an object returned by `simGames`, these are `print`, `summary` and `plot`, example use is show below.

### Example

```{r}
egGames <- simGames(n = 10, p = .78, p2 = .56, firstServe = .67)
```
The object `egGames` has a class of **`r class(egGames)[2]`** which comes with a few methods

```{r}
egGames
summary(egGames)
plot(egGames)
```

### Using `simDf`

The returned list can also be entered into the function [`simDf`](simDf.html) which will convert the simulated games into a dataset.

```{r}
df <- simDf(egGames)
head(df)
```

The variables in the dataset are:

variables | about
----------|------
simNo | simulation number
player | player name
p | probability of server winning a point on their first serve
p2 | probability of server winning a point on their second serve
firstServe | probability of first serve being in
result | game result (1 if server wins, 0 if returner wins)
server | number of points won by server in service game
returner | number of points won by returner in service game


<a href="https://github.com/durtal/servevolleyR" class="github-corner"><svg width="80" height="80" viewBox="0 0 250 250" style="fill:#d9230f; color:#fcfcfc; position: absolute; top: 0; border: 0; right: 0;"><path d="M0,0 L115,115 L130,115 L142,142 L250,250 L250,0 Z"></path><path d="M128.3,109.0 C113.8,99.7 119.0,89.6 119.0,89.6 C122.0,82.7 120.5,78.6 120.5,78.6 C119.2,72.0 123.4,76.3 123.4,76.3 C127.3,80.9 125.5,87.3 125.5,87.3 C122.9,97.6 130.6,101.9 134.4,103.2" fill="currentColor" style="transform-origin: 130px 106px;" class="octo-arm"></path><path d="M115.0,115.0 C114.9,115.1 118.7,116.5 119.8,115.4 L133.7,101.6 C136.9,99.2 139.9,98.4 142.2,98.6 C133.8,88.0 127.5,74.4 143.8,58.0 C148.5,53.4 154.0,51.2 159.7,51.0 C160.3,49.4 163.2,43.6 171.4,40.1 C171.4,40.1 176.1,42.5 178.8,56.2 C183.1,58.6 187.2,61.8 190.9,65.4 C194.5,69.0 197.7,73.2 200.1,77.6 C213.8,80.2 216.3,84.9 216.3,84.9 C212.7,93.1 206.9,96.0 205.4,96.6 C205.1,102.4 203.0,107.8 198.3,112.5 C181.9,128.9 168.3,122.5 157.7,114.1 C157.9,116.9 156.7,120.9 152.7,124.9 L141.0,136.5 C139.8,137.7 141.6,141.9 141.8,141.8 Z" fill="currentColor" class="octo-body"></path></svg></a><style>.github-corner:hover .octo-arm{animation:octocat-wave 560ms ease-in-out}@keyframes octocat-wave{0%,100%{transform:rotate(0)}20%,60%{transform:rotate(-25deg)}40%,80%{transform:rotate(10deg)}}@media (max-width:500px){.github-corner:hover .octo-arm{animation:none}.github-corner .octo-arm{animation:octocat-wave 560ms ease-in-out}}</style>
