---
title: "simGames"
---
```{r echo=FALSE, warning=FALSE, message=FALSE}
library(servevolleyR)
```

Simulate many service games given a number of parameters for the server, that include probability of the server winning a point on their first serve, on their second serve, and the probability that their first serve will go in, returning a detailed list.

### Usage

```{r eval=FALSE}
simGames(n = 1e3, p, p2 = NULL, firstServe = NULL, detail = FALSE, player = "A")
```

### Arguments

param | details
------|--------
n | number of simulations (default is 1000)
p | probability of server winning point on their first serve
p2 | probability of server winning point on their second serve
firstServe | probability of first serve being in
player | player name
.progress | `plyr`'s  progress bar

### Return

Unlike using `replicate` on `simGame`, using `simGames` will return a detailed list, containing data about the simulated games rather than just the results of those simulations

### Methods

There are a number of generic methods available for an object returned by `simGames`, these are `print`, `summary` and `plot`, example use is show below.

### Example

```{r}
egGames <- simGames(n = 10, p = .78, p2 = .56, firstServe = .67)
```
The object `egGames` has a class of **`r class(egGames)[2]`** which comes with a few methods

```{r}
egGames
summary(egGames)
plot(egGames)
```

The returned list can also be entered into the function [`simDf`](simDf.html) which will convert the simulated games into a dataframe.

```{r}
df <- simDf(egGames)
head(df)
```
