---
title: "simGame"
---
```{r echo=FALSE, warning=FALSE, message=FALSE}
library(servevolleyR)
```

Simulate a service game given a number of parameters for the server, that include probability of the server winning a point on their first serve, on their second serve, and the probability that their first serve will go in.

### Usage

```{r eval=FALSE}
simGame(p, p2 = NULL, firstServe = NULL, detail = FALSE, player = "A")
```

### Arguments

param | details | default
------|---------|--------
p | probability of server winning point on their first serve |
p2 | probability of server winning point on their second serve | `NULL`
firstServe | probability of first serve being in | `NULL`
detail | return a detailed list about the game, including service probabilities, points won, and result | `FALSE`
player | player name | "A"

### Return

The default function returns a 1, if the server wins the game, or 0, if the returner wins the game.  If `detail` argument is changed to `TRUE`, then the function will return a list with details about the simulated game, including service probabilities, points won by the server and returner, and the result (1 or 0)

### Methods

There are a number of generic methods available for an object returned by `simGame`, these are `print` and `summary`, example use is show below.

### Example

```{r}
simGame(p = .78, p2 = .56, firstServe = .67)
# a look at a detailed return
game <- simGame(p = .78, p2 = .56, firstServe = .67, detail = TRUE)
```
The object `game` has a class of **`r class(game)[2]`** which comes with a few methods

```{r}
game

summary(game)
```

To simulate many games, you can either use `replicate`, as shown below which is used with `detail = FALSE`, or [simGames](simGames.html) which will return a detailed list with data about the simulated games, rather than just the result.

```{r}
game <- replicate(1e3, simGame(p = .78, p2 = .56, firstServe = .67))
head(game)
# summarise results
table(game) / sum(table(game))
```

### Using `simDf`

If the function is called with `detail = TRUE`, then the list returned can be converted into a dataset using the [simDf](simDf.html) function, producing a dataset containing the following variables:

variables | about
----------|------
player | player name
p | probability of server winning a point on their first serve
p2 | probability of server winning a point on their second serve
firstServe | probability of first serve being in
result | game result (1 if server wins, 0 if returner wins)
server | number of points won by server in service game
returner | number of points won by returner in service game
