---
title: "simMatches"
---
```{r echo=FALSE, warning=FALSE, message=FALSE}
library(servevolleyR)
```

Simulate many matches between two players, given a number of parameters, that include probability of each player winning a point on their first serve, on their second serve, and the probability that their first serve will go in.  This function returns a detailed list with data about the sets and games within each simulated match.

### Usage

```{r eval=FALSE}
simMatches(n = 1000, pA, pB, sets = c(3, 5), tiebreaks = TRUE,
           finalSetTiebreak = FALSE, players = c("A", "B"),
           p2A = NULL, firstServeA = NULL,
           p2B = NULL, firstServeB = NULL,
           .progress = "none")
```

### Arguments

param | details
------|--------
n | number of simulations (default is 1000)
pA | probability of player A winning point on their first serve
pB | probability of player B winning point on their first serve
sets | number of sets (3 or 5)
tiebreaks | play tiebreaks in the event the set reaches 6 games all (default = TRUE)
finalSetTiebreak | play a final set tiebreak if sets and games are tied, otherwise keep playing
players | player names (vector of length 2)
p2A | probability of player A winning point on their second serve
firstServeA | probability of player A's first serve being in
p2A | probability of player B winning point on their second serve
firstServeB | probability of player B's first serve being in
.progress | `plyr`'s  progress bar

### Return

Unlike using `replicate` on `simMatch`, using `simMatches` will return a detailed list, containing data about the simulated matches rather than just the results of those simulations.

### Methods

There are a number of generic methods available for an object returned by `simMatches`, these are `print`, `summary` and `plot`, example use is show below.

### Example

```{r}
egMatches <- simMatches(n = 100, sets = 3,
                        pA = .78, pB = .70,
                        p2A = .56, firstServeA = .67,
                        p2B = .6, firstServeB = .7)
```
The object `egMatches` has a class of **`r class(egMatches)[2]`** which comes with a few methods

```{r}
egMatches
summary(egMatches)
plot(egMatches)
```

```{r echo=FALSE}
df <- simDf(egMatches)
head(df)
```

The returned list can also be entered into the function [`simDf`](simDf.html) which will convert the simulated matches into a dataframe, containing data about each of the simulations, including data going all the way down to the individual games.  `egMatches` contains **100** simulations, which produces a dataset of dimensions `r dim(egMatches)`.

```{r eval=FALSE}
df <- simDf(egMatches)
```
```{r}
head(df)
```
