---
title: "simMatch"
---
```{r echo=FALSE, warning=FALSE, message=FALSE}
library(servevolleyR)
```

Simulate a match between two players, given a number of parameters, that include probability of each player winning a point on their first serve, on their second serve, and the probability that their first serve will go in.

### Usage

```{r eval=FALSE}
simMatch(pA, pB, sets = c(3, 5), tiebreaks = TRUE,
         finalSetTiebreak = FALSE, players = c("A", "B"), detail = FALSE,
         p2A = NULL, firstServeA = NULL,
         p2B = NULL, firstServeB = NULL)
```

### Arguments

param | details | default
------|---------|--------
pA | probability of player A winning point on their first serve |
pB | probability of player B winning point on their first serve |
sets | number of sets (3 or 5) |
tiebreaks | play tiebreaks in the event the set reaches 6 games all | `TRUE`
finalSetTiebreak | play a final set tiebreak if sets and games are tied, otherwise keep playing | `FALSE`
players | player names (vector of length 2) | c("A", "B")
detail | return a detailed list about the match, including service probabilities, sets won, set data, games won, game data and result | `FALSE`
p2A | probability of player A winning point on their second serve | `NULL`
firstServeA | probability of player A's first serve being in | `NULL`
p2A | probability of player B winning point on their second serve | `NULL`
firstServeB | probability of player B's first serve being in | `NULL`

### Return

The default function returns a 1, if player A wins the match, or 0, if player B wins the match.  If `detail` argument is changed to `TRUE`, then the function will return a list with details about the simulated match, including service probabilities, sets and games won by each player, and the result (1 or 0)

### Methods

There are a number of generic methods available for an object returned by `simMatch`, these are `print` and `summary`, example use is show below.

### Example

```{r}
simMatch(sets = 3, finalSetTiebreak = TRUE,
         pA = .78, pB = .70,
         p2A = .56, firstServeA = .67,
         p2B = .6, firstServeB = .7)
```

Adding `detail = TRUE` will return a detailed list with data about the simulated match.

```{r}
egMatch <- simMatch(sets = 3, finalSetTiebreak = TRUE, detail = TRUE,
                    pA = .78, pB = .70,
                    p2A = .56, firstServeA = .67,
                    p2B = .6, firstServeB = .7)
```
The object `egMatch` has a class of **`r class(egMatch)[2]`** which comes with a print method

```{r}
egMatch
```

### Using `simDf`

If the function is called with `detail = TRUE`, then the list returned can be converted into a dataset using the [simDf](simDf.html) function:

```{r}
df <- simDf(egMatch)
head(df)
```

The dataset contains the following variables:

variables | about
----------|------
playerA | player A (who started the match serving)
playerB | player B (who started the match returning)
mA | sets won by player A
mB | sets won by player B
result | match result, (1 if player A wins, 0 otherwise)
setNo | set number
pA | player A (who started the set serving)
pB | player B (who started the set returning)
setA | games won by player A
setB | games won by player B
set_res | set result (1 if player A wins, 0 if player B wins)
gameNo | game number in set
serving | player serving
p | probability of server winning a point on their first serve
p2 | probability of server winning a point on their second serve
firstServe | probability of first serve being in
game_res | game result (1 if server wins, 0 if returner wins)
server | number of points won by server in service game
returner | number of points won by returner in service game
