---
title: "simSet"
---
```{r echo=FALSE, warning=FALSE, message=FALSE}
library(servevolleyR)
```

Simulate a set between two players given a number of parameters, that include probability of each player winning a point on their first serve, on their second serve, and the probability that their first serve will go in.

### Usage

```{r eval=FALSE}
simSet(pA, pB,
       playTiebreak = TRUE, players = c("A", "B"),
       p2A = NULL, firstServeA = NULL,
       p2B = NULL, firstServeB = NULL)
```

### Arguments

param | details
------|--------
pA | probability of player A winning point on their first serve
pB | probability of player B winning point on their first serve
playTiebreak | play tiebreak in the event the set reaches 6 games all
players | player names (vector of length 2)
detail | return a detailed list about the set, including service probabilities, games won, game data and result
p2A | probability of player A winning point on their second serve
firstServeA | probability of player A's first serve being in
p2A | probability of player B winning point on their second serve
firstServeB | probability of player B's first serve being in

### Return

The default function returns a 1, if the server wins the set, or 0, if the returner wins the set.  If `detail` argument is changed to `TRUE`, then the function will return a list with details about the simulated set, including service probabilities, games won by each player, and the result (1 or 0)

### Methods

There are a number of generic methods available for the detailed list returned by `simSet`, these are `print` and `summary`, example use is show below.

### Example

```{r}
simSet(pA = .78, pB = .70, p2A = .56, p2B = .6,
       firstServeA = .67, firstServeB = .7)
egSet <- simSet(pA = .78, pB = .70, p2A = .56, p2B = .6,
                firstServeA = .67, firstServeB = .7, detail = TRUE)
```
The object `egSet` has a class of **`r class(egSet)[2]`** which comes with a few methods

```{r}
egSet
summary(egSet)
```

### Using `simDf`

If `detail = TRUE` then the list can also be entered into the function [`simDf`](simDf.html) which will convert the simulated set into a dataframe.

```{r}
df <- simDf(egSet)
df
```

The dataset contains the following variables:

variables | about
----------|------
pA | player A
pB | player B
setA | games won by player A
setB | games won by player B
set_res | set result (1 if player A wins, 0 if player B wins)
gameNo | game number in set
serving | player serving
p | probability of server winning a point on their first serve
p2 | probability of server winning a point on their second serve
firstServe | probability of first serve being in
game_res | game result (1 if server wins, 0 if returner wins)
server | number of points won by server in service game
returner | number of points won by returner in service game
