---
title: "simSets"
---
```{r echo=FALSE, warning=FALSE, message=FALSE}
library(servevolleyR)
```

Simulate many sets between two players given a number of parameters, that include probability of each player winning a point on their first serve, on their second serve, and the probability that their first serve will go in.  This function returns a detailed list with data about the games within each simulated set.

### Usage

```{r eval=FALSE}
simSets(n = 1000, pA, pB,
        playTiebreak = TRUE, players = c("A", "B"),
        p2A = NULL, firstServeA = NULL,
        p2B = NULL, firstServeB = NULL,
        .progress = "none")
```

### Arguments

param | details
------|--------
n | number of simulations (default is 1000)
pA | probability of player A winning point on their first serve
pB | probability of player B winning point on their first serve
playTiebreak | play tiebreak in the event the set reaches 6 games all
players | player names (vector of length 2)
p2A | probability of player A winning point on their second serve
firstServeA | probability of player A's first serve being in
p2A | probability of player B winning point on their second serve
firstServeB | probability of player B's first serve being in
.progress | `plyr`'s  progress bar

### Return

Unlike using `replicate` on `simSet`, using `simSets` will return a detailed list, containing data about the simulated sets rather than just the results of those simulations.

### Methods

There are a number of generic methods available for an object returned by `simSets`, these are `print`, `summary` and `plot`, example use is show below.

### Example

```{r}
egSets <- simSets(n = 100,
                  pA = .78, pB = .70, p2A = .56, p2B = .6,
                  firstServeA = .67, firstServeB = .7)
```
The object `egSets` has a class of **`r class(egSets)[2]`** which comes with a few methods

```{r}
egSets
summary(egSets)
plot(egSets)
```

### Using `simDf`

If `detail = TRUE` then the list can also be entered into the function [`simDf`](simDf.html) which will convert the simulated sets into a dataframe.

```{r}
df <- simDf(egSets)
head(df)
```

The dataset contains the following variables:

variables | about
----------|------
simNo | simulation number
pA | player A
pB | player B
setA | games won by player A
setB | games won by player B
set_res | set result (1 if player A wins, 0 if player B wins)
gameNo | game number in set
serving | player serving
p | probability of server winning a point on their first serve
p2 | probability of server winning a point on their second serve
firstServe | probability of first serve being in
game_res | game result (1 if server wins, 0 if returner wins)
server | number of points won by server in service game
returner | number of points won by returner in service game

<a href="https://github.com/durtal/servevolleyR" class="github-corner"><svg width="80" height="80" viewBox="0 0 250 250" style="fill:#d9230f; color:#fcfcfc; position: absolute; top: 0; border: 0; right: 0;"><path d="M0,0 L115,115 L130,115 L142,142 L250,250 L250,0 Z"></path><path d="M128.3,109.0 C113.8,99.7 119.0,89.6 119.0,89.6 C122.0,82.7 120.5,78.6 120.5,78.6 C119.2,72.0 123.4,76.3 123.4,76.3 C127.3,80.9 125.5,87.3 125.5,87.3 C122.9,97.6 130.6,101.9 134.4,103.2" fill="currentColor" style="transform-origin: 130px 106px;" class="octo-arm"></path><path d="M115.0,115.0 C114.9,115.1 118.7,116.5 119.8,115.4 L133.7,101.6 C136.9,99.2 139.9,98.4 142.2,98.6 C133.8,88.0 127.5,74.4 143.8,58.0 C148.5,53.4 154.0,51.2 159.7,51.0 C160.3,49.4 163.2,43.6 171.4,40.1 C171.4,40.1 176.1,42.5 178.8,56.2 C183.1,58.6 187.2,61.8 190.9,65.4 C194.5,69.0 197.7,73.2 200.1,77.6 C213.8,80.2 216.3,84.9 216.3,84.9 C212.7,93.1 206.9,96.0 205.4,96.6 C205.1,102.4 203.0,107.8 198.3,112.5 C181.9,128.9 168.3,122.5 157.7,114.1 C157.9,116.9 156.7,120.9 152.7,124.9 L141.0,136.5 C139.8,137.7 141.6,141.9 141.8,141.8 Z" fill="currentColor" class="octo-body"></path></svg></a><style>.github-corner:hover .octo-arm{animation:octocat-wave 560ms ease-in-out}@keyframes octocat-wave{0%,100%{transform:rotate(0)}20%,60%{transform:rotate(-25deg)}40%,80%{transform:rotate(10deg)}}@media (max-width:500px){.github-corner:hover .octo-arm{animation:none}.github-corner .octo-arm{animation:octocat-wave 560ms ease-in-out}}</style>
