---
title: "simSets"
---
```{r echo=FALSE, warning=FALSE, message=FALSE}
library(servevolleyR)
```

Simulate many sets between two players given a number of parameters, that include probability of each player winning a point on their first serve, on their second serve, and the probability that their first serve will go in.  This function returns a detailed list with data about the games within each simulated set.

### Usage

```{r eval=FALSE}
simSets(n = 1000, pA, pB,
        playTiebreak = TRUE, players = c("A", "B"),
        p2A = NULL, firstServeA = NULL,
        p2B = NULL, firstServeB = NULL,
        .progress = "none")
```

### Arguments

param | details
------|--------
n | number of simulations (default is 1000)
pA | probability of player A winning point on their first serve
pB | probability of player B winning point on their first serve
playTiebreak | play tiebreak in the event the set reaches 6 games all
players | player names (vector of length 2)
p2A | probability of player A winning point on their second serve
firstServeA | probability of player A's first serve being in
p2A | probability of player B winning point on their second serve
firstServeB | probability of player B's first serve being in
.progress | `plyr`'s  progress bar

### Return

Unlike using `replicate` on `simSet`, using `simSets` will return a detailed list, containing data about the simulated sets rather than just the results of those simulations.

### Methods

There are a number of generic methods available for an object returned by `simSets`, these are `print`, `summary` and `plot`, example use is show below.

### Example

```{r}
egSets <- simSets(n = 100,
                  pA = .78, pB = .70, p2A = .56, p2B = .6,
                  firstServeA = .67, firstServeB = .7)
```
The object `egSets` has a class of **`r class(egSets)[2]`** which comes with a few methods

```{r}
egSets
summary(egSets)
plot(egSets)
```

The returned list can also be entered into the function [`simDf`](simDf.html) which will convert the simulated games into a dataframe.

```{r}
df <- simDf(egSets)
head(df)
```
