---
title: "simTiebreak"
---
```{r echo=FALSE, warning=FALSE, message=FALSE}
library(servevolleyR)
```

Simulate a tiebreak at the end of a set, given a number of parameters, that include probability of each player winning a point on their first serve, on their second serve, and the probability that their first serve will go in.

### Usage

Player A serves first in the tiebreak, after which each player serves two points each.

```{r eval=FALSE}
simTiebreak(pA, pB, p2A = NULL, firstServeA = NULL, p2B = NULL, firstServeB = NULL)
```

### Arguments

param | details
------|--------
pA | probability of player A winning point on their serve
pB | probability of player B winning point on their serve
p2A | probability of player A winning point on their second serve
firstServeA | probability of player A getting their first serve in
p2B | probability of player B winning point on their second serve
firstServeB | probability of player B getting their first serve in

### Return

This function returns 1, if player A wins the game, or 0 if player B wins the game.

### Example

```{r}
simTiebreak(pA = .76, pB = .67)
# simulate many tiebreaks
tiebreak <- replicate(1e3, simTiebreak(pA = .76, pB = .67))
table(tiebreak) / sum(table(tiebreak))
```
